### 2007-01-16 Documentation/appendix.tex
JK - Minor corrections in appendix B

\begin{appendix}

\chapter{\GLOBES\ installation}
\label{app:installation}
\index{norm}{Installation|(}

\section*{Prerequisites for installation of \GLOBES}

@@

\section*{Installation Instructions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Catalogue of {\sf AEDL}-Files}
\label{app:aedlfiles}
Along with the \GLOBES\ package comes a catalogue of pre-defined experiment \AEDL\ files for different
future experiments and different beam and detector technologies. These include the planned superbeam experiments
and their possible upgrades, different reactor experiment setups, different $\beta$-beam setups, and different 
neutrino factory setups. A complete list
of all pre-defined experiment files an be found in \tabl{experiments}. More detailed descriptions of the
corresponding files, the assumptions, requirements, and references are given in the following.

@@

possible the LOI \cite{Itow:2001ee} and the basic version was used within \cite{Huber:2002mx}. These references

@@

The file {\tt Reactor1.glb} allows to simulate a small $\bar{\nu}_e$-disappearance reactor experiment. The basic
version of this file was used within \cite{Huber:2003pm} which should be cited if the file {\tt Reactor1.glb} is
used for a scientific publication or a talk. For calculations that involve {\tt Reactor1.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The neutrino source is the core of a nuclear power reactor. The integrated luminosity is assumed to be
$\mathrm{\mathcal{L} = 400 \,t \, GW\, yr}$, \eg\ a 20~t detector, a reactor with a thermal power of 4~GW
and a running period of 5 years. As detector technology a liquid scintillator 
detector is assumed, a far detector at a baseline of L~=~1.7~km and a near detector which is
assumed to be identical to the far detector (maybe apart from the size) in order to minimize the impact of systematical uncertainties. The normalization error
used in the file {\tt Reactor1.glb} has to be considered as an effective error, receiving contributions from
individual uncertainties (see~\cite{Huber:2003pm}). The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt Reactor1.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & \hspace{5.5cm} & 0.008 & 0.005\\
 & &  & &\\
Background & $5.8\cdot 10^{-5} \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_\mathrm{CC}$ & \hspace{5.5cm} &
$10^{-6}$ & $10^{-6}$ \\ \hline \hline 
\end{tabular}
\end{center}

@@

The files {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} allow to simulate the \DC\ reactor experiment in France. 
The basic version of these files were used within \cite{Huber:2006vr} which should be cited if the files 
{\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} are
used for a scientific publication or a talk. For calculations that involve {\tt D-Chooz\_near.glb} and/or {\tt D-Chooz\_far.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The \DC\ experiment is located at the Chooz reactor complex and the two reactor cores serve as $\bar{\nu}_e$
neutrino source, so the thermal power is $\mathrm{2\cdot4.2\,GW}$. Two identical liquid scintillator detectors
with a fiducial mass of $\mathrm{m_{det} = 10.16 \,t}$ are used as near and far detector. The far detector
is planned to be located in the {\sc Chooz} cavern at a baseline of L~=~1.05~km from the two reactor cores and
the near detector is assumed to be located at a distance of 0.1~km to the cores. The total running time of the
experiment is assumed to be 5 years. So, the integrated luminosity at the far detector yields $\mathrm{\mathcal{L} \approx
427 \,t \, GW\, yr}$.
Here, the total running time of 5 years is assumed within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}, so near
and far detector are assumed to start the mode of operation simultaneously. For the simulation of \DC\ and
considering a delayed start of data taking at the near detector the file {\tt D-Chooz\_near.glb} has to be
modified. The cancellation of systematical uncertainties is considered by the manual definition of a $\chi^2$
as described in \cite{Huber:2006vr} with the treatment of user-defined systematics as described in \Sec~\ref{sec:userchi}   
The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|c|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{flux}$ & $\sigma^N_\mathrm{fid}$ & $\sigma^F_\mathrm{fid}$ &
$\sigma^N_\mathrm{cal}$ & $\sigma^F_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & & 0.02 & 0.006 & 0.006 & 0.005 &
0.005 \\
 & & & & & & & \\
Background & neglected & (sys. dominates) & -- & -- & -- & -- & -- \\ \hline \hline 
\end{tabular}
\end{center}

@@

A variable neutrino factory scenario can be simulated with the file {\tt NFvar.glb}. The basic version was
used within \cite{Huber:2006wb} and follows the neutrino factory scenarios from \cite{Huber:2002mx}. These
references should be cited if the file {\tt
NFvar.glb} is used for a scientific publication or a talk. For calculations that involve {\tt
NFvar.glb}, the following additional files are required:
\bi
\item {\tt ThresholdEnergies.dat} (list of energies)
\item {\tt CIDthreshold.dat} (list for CID threshold)
\item {\tt MINOSthreshold.dat} (list for MINOS threshold)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
and the values of the following {\sf AEDL}-Variables have to be set:
\bi
\item {\tt emax} (parent energy of the stored muons $\left[\mathrm{km}\right]$)
\item {\tt BASELINE} (experiment baseline $\left[\mathrm{GeV}\right]$)
\ei
The neutrino beam is produced by the decay of muons stored in a storage ring at a parent energy of
$\mathrm{E_\mu =}$~{\tt emax}. The parent energy of the muons can be set in the range
$\mathrm{10\,GeV\lesssim E_\mu\lesssim 80\, GeV}$. The baseline of the scenario is L~=~{\tt BASELINE}. 
Besides these settings the other attributes of {\tt NFvar.glb} are similar to the ones from {\tt
NFstandard.glb}. Only the treatment of the disappearance channels is different. Whereas the CID threshold is
also applied in the disappearance channels of {\tt NFstandard.glb} this is not the case for the disapperance
channel definition within {\tt NFvar.glb} where no CID is applied and a threshold similar to the threshold of
the MINOS experiment \cite{Ables:1995wq} is applied. The following rules are defined within
{\tt NFvar.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.9 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0\cdot 10^{-5} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.2 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^+$-stored} & & \\ \hline
Signal &  $0.45 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.025 & $10^{-4}$ \\
 & & & & \\
Background &  $5.0\cdot 10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ &  $5.0\cdot
10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow\bar{\nu}_\mu)_\mathrm{CC}$ & 0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^-$-stored} & & \\ \hline
Signal &  $0.9 \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\bar{\nu}_e
\rightarrow \bar{\nu}_\mu)_\mathrm{CC}$& 0.025& $10^{-4}$\\
 & & & & \\
Background &  $1.0\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^-$-stored} & & \\ \hline
Signal & $0.35 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$  & & 0.025& $10^{-4}$\\
 & & & & \\
Background &  $5.0\cdot 10^{-6} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $5.0\cdot 10^{-6} \, \otimes \, (\nu_\mu \rightarrow
\nu_\mu)_\mathrm{CC}$  & 0.2& $10^{-4}$\\ \hline \hline
\end{tabular}
\end{center}

@@

A variable neutrino factory scenario that includes the golden and silver appearance channels can be 
simulated with the file {\tt NF\_GoldSilver.glb}. The basic version was
used within \cite{Huber:2006wb} and the golden channel follows the neutrino factory scenarios from \cite{Huber:2002mx}
and the description of the silver channel follows \cite{Autiero:2003fu}. These
references should be cited if the file {\tt
NFvar\_GoldSilver.glb} is used for a scientific publication or a talk. For calculations that involve {\tt
NFvar\_GoldSilver.glb}, the following additional files are required:
\bi
\item {\tt ThresholdEnergies.dat} (list of energies)
\item {\tt CIDthreshold.dat} (list for CID threshold)
\item {\tt MINOSthreshold.dat} (list for MINOS threshold)
\item {\tt ECCthreshold.dat} (list for ECC threshold)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
and the values of the following {\sf AEDL}-Variables have to be set:
\bi
\item {\tt emax} (parent energy of the stored muons $\left[\mathrm{km}\right]$)
\item {\tt BASELINE} (experiment baseline $\left[\mathrm{GeV}\right]$)
\ei
The beam and golden channel attributes are similar to {\tt NFvar.glb}. The parent energy of the muons can be set
in the range $\mathrm{10\,GeV\lesssim E_\mu\lesssim 80\, GeV}$. The baseline is set by the {\sf
AEDL}-Variable {\tt BASELINE}. For the silver channel an additional ECC detector with a fiducial mass
$\mathrm{m_{ECC} = 5\,kt}$ is assumed to be located at the same baseline as the MID detector. The energy
resolution of the silver channel is set to $\mathrm{\sigma_e=20\%\cdot E}$. The following additional rule
compared to {\tt NFvar.glb} is introduced to {\tt NF\_GoldSilver.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{$\tau$-Appearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.096 \, \otimes \, (\nu_e \rightarrow \nu_\tau)_\mathrm{CC}$ & & 0.15 & $10^{-4}$ \\
 & & & & \\
Background & $3.1\cdot 10^{-8} \, \otimes \, (\nu_e \rightarrow \nu_e)_\mathrm{CC}$ & $2.0\cdot 10^{-8} \,
\otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.2 & $10^{-4}$ \\ 
 & $3.7\cdot 10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $1.0\cdot 10^{-3} \,
 \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\tau)_\mathrm{CC}$& 0.2 & $10^{-4}$ \\ 
 & $7.0 \cdot 10^{-7} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $7.0\cdot 10^{-7} \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$& 0.2 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

@@

A variable neutrino factory hybrid detector scenario can be simulated with the file {\tt NF\_hR\_lT.glb}. The basic version was
used within \cite{Huber:2006wb} and follows the neutrino factory scenarios from \cite{Huber:2002mx}. These
references should be cited if the file {\tt NF\_hR\_lT.glb} is used for a scientific publication or a talk.
For calculations that involve {\tt NF\_hR\_lT.glb}, the same additional files as for {\tt NFvar.glb} are
required and the {\sf AEDL}-Variables {\tt emax} and {\tt BASELINE} have to be set. {\tt NF\_hR\_lT.glb} 
implements a lower threshold ($\mathrm{\sim\,1\,GeV}$) at a higher energy resolution
$\mathrm{\sigma_e=15\%\cdot E + 0.085\, MeV}$ where the constant term represents 
the effects from Fermi Motion. The background rejection is introduced energy dependent as 
$10^{-3}/\mathrm{E^2}$ and matches {\tt NFvar.glb} at higher energies. The following rules are defined within {\tt NF\_hR\_lT.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.9 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.2 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^+$-stored} & & \\ \hline
Signal &  $0.5 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.025 & $10^{-4}$ \\
 & & & & \\
Background &  $1.0 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & (energy dep. rejection)
& 0.2 & $10^{-4}$\\
 &  $1.0 \, \otimes \, (\bar{\nu}_\mu \rightarrow\bar{\nu}_\mu)_\mathrm{CC}$ & (energy dep. rejection)
&0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^-$-stored} & & \\ \hline
Signal &  $0.9 \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\bar{\nu}_e
\rightarrow \bar{\nu}_\mu)_\mathrm{CC}$& 0.025& $10^{-4}$\\
 & & & & \\
Background &  $1.0\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^-$-stored} & & \\ \hline
Signal & $0.5 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$  & & 0.025& $10^{-4}$\\
 & & & & \\
Background &  $1.0 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & (energy dep. rejection)
& 0.2 & $10^{-4}$\\
 & $1.0 \, \otimes \, (\nu_\mu \rightarrow
\nu_\mu)_\mathrm{CC}$  & (energy dep. rejection)
&0.2& $10^{-4}$\\ \hline \hline
\end{tabular}
\end{center}

@@

\end{appendix}

>>>>

%\begin{appendix}
\appendix
\chapter{\GLOBES\ installation}
\label{app:installation}
\index{norm}{Installation|(}

\section{Prerequisites for installation of \GLOBES}

@@

\section{Installation Instructions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Catalogue of {\sf AEDL}-Files}
\label{app:aedlfiles}
Along with the \GLOBES\ package comes a catalogue of pre-defined experiment \AEDL\ files for different
future experiments and different beam and detector technologies. These include the planned superbeam experiments
and their possible upgrades, different reactor experiment setups, different $\beta$-beam setups, and different 
neutrino factory setups. A complete list
of all pre-defined experiment files can be found in \tabl{experiments}. More detailed descriptions of the
corresponding files, the assumptions, requirements, and references are given in the following.

@@

possible the LOI \cite{Itow:2001ee}, and the basic version was used within \cite{Huber:2002mx}. These references

@@

The file {\tt Reactor1.glb} allows to simulate a small $\bar{\nu}_e$-disappearance reactor experiment. The basic
version of this file was used within \cite{Huber:2003pm} which should be cited if the file {\tt Reactor1.glb} is
used for a scientific publication or a talk. For calculations that involve {\tt Reactor1.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The neutrino source is the core of a nuclear power reactor. The integrated luminosity is assumed to be
$\mathrm{\mathcal{L} = 400 \,t \, GW\, yr}$, \eg\ a 20~t detector, a reactor with a thermal power of 4~GW
and a running period of 5 years. As detector technology, a liquid scintillator 
detector is assumed, a far detector at a baseline of L~=~1.7~km and a near detector which is
assumed to be identical to the far detector (maybe apart from the size) in order to minimize the impact of systematical uncertainties. The normalization error
used in the file {\tt Reactor1.glb} has to be considered as an effective error, receiving contributions from
individual uncertainties (see~\cite{Huber:2003pm}). The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt Reactor1.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & \hspace{5.5cm} & 0.008 & 0.005\\
 & &  & &\\
Background & $5.8\cdot 10^{-5} \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_\mathrm{CC}$ & \hspace{5.5cm} &
$10^{-6}$ & $10^{-6}$ \\ \hline \hline 
\end{tabular}
\end{center}

@@

The files {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} allow to simulate the \DC\ reactor experiment in France. 
The basic versions of these files were used within \cite{Huber:2006vr}, which should be cited if the files 
{\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} are
used for a scientific publication or a talk. For calculations that involve {\tt D-Chooz\_near.glb} and/or {\tt D-Chooz\_far.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The \DC\ experiment is located at the Chooz reactor complex, and the two reactor cores serve as $\bar{\nu}_e$
neutrino source, so the thermal power is $\mathrm{2\cdot4.2\,GW}$. Two identical liquid scintillator detectors
with a fiducial mass of $\mathrm{m_{det} = 10.16 \,t}$ are used as near and far detector. The far detector
is planned to be located in the {\sc Chooz} cavern at a baseline of L~=~1.05~km from the two reactor cores and
the near detector is assumed to be located at a distance of 0.1~km to the cores. The total running time of the
experiment is assumed to be 5 years. So, the integrated luminosity at the far detector yields $\mathrm{\mathcal{L} \approx
427 \,t \, GW\, yr}$.
Here, the total running time of 5 years is assumed within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}, so near
and far detector are assumed to start the mode of operation simultaneously. For the simulation of \DC\ and
considering a delayed start of data taking at the near detector the file {\tt D-Chooz\_near.glb} has to be
modified. The cancellation of systematical uncertainties is considered by the manual definition of a $\chi^2$
as described in \cite{Huber:2006vr} with the treatment of user-defined systematics as described in \Sec~\ref{sec:userchi}   
The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|c|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{flux}$ & $\sigma^N_\mathrm{fid}$ & $\sigma^F_\mathrm{fid}$ &
$\sigma^N_\mathrm{cal}$ & $\sigma^F_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & & 0.02 & 0.006 & 0.006 & 0.005 &
0.005 \\
 & & & & & & & \\
Background & neglected & (sys. dominates) & -- & -- & -- & -- & -- \\ \hline \hline 
\end{tabular}
\end{center}

@@

A variable neutrino factory scenario can be simulated with the file {\tt NFvar.glb}. The basic version was
used within \cite{Huber:2006wb} and follows the neutrino factory scenarios from \cite{Huber:2002mx}. These
references should be cited if the file {\tt
NFvar.glb} is used for a scientific publication or a talk. For calculations that involve {\tt
NFvar.glb}, the following additional files are required:
\bi
\item {\tt ThresholdEnergies.dat} (list of energies)
\item {\tt CIDthreshold.dat} (list for CID threshold)
\item {\tt MINOSthreshold.dat} (list for MINOS threshold)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
and the values of the following {\sf AEDL}-Variables have to be set:
\bi
\item {\tt emax} (parent energy of the stored muons $\left[\mathrm{km}\right]$)
\item {\tt BASELINE} (experiment baseline $\left[\mathrm{GeV}\right]$)
\ei
The neutrino beam is produced by the decay of muons stored in a storage ring at a parent energy of
$\mathrm{E_\mu =}$~{\tt emax}. The parent energy of the muons can be set in the range
$\mathrm{10\,GeV\lesssim E_\mu\lesssim 80\, GeV}$. The baseline of the scenario is L~=~{\tt BASELINE}. 
Besides these settings the other attributes of {\tt NFvar.glb} are similar to the ones from {\tt
NFstandard.glb}. Only the treatment of the disappearance channels is different. Whereas the CID threshold is
also applied in the disappearance channels of {\tt NFstandard.glb}, this is not the case for the disapperance
channel definition within {\tt NFvar.glb}, where no CID is applied, and a threshold similar to the threshold of
the MINOS experiment \cite{Ables:1995wq} is applied. The following rules are defined within
{\tt NFvar.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.9 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0\cdot 10^{-5} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.2 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^+$-stored} & & \\ \hline
Signal &  $0.45 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.025 & $10^{-4}$ \\
 & & & & \\
Background &  $5.0\cdot 10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ &  $5.0\cdot
10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow\bar{\nu}_\mu)_\mathrm{CC}$ & 0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^-$-stored} & & \\ \hline
Signal &  $0.9 \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\bar{\nu}_e
\rightarrow \bar{\nu}_\mu)_\mathrm{CC}$& 0.025& $10^{-4}$\\
 & & & & \\
Background &  $1.0\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^-$-stored} & & \\ \hline
Signal & $0.35 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$  & & 0.025& $10^{-4}$\\
 & & & & \\
Background &  $5.0\cdot 10^{-6} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $5.0\cdot 10^{-6} \, \otimes \, (\nu_\mu \rightarrow
\nu_\mu)_\mathrm{CC}$  & 0.2& $10^{-4}$\\ \hline \hline
\end{tabular}
\end{center}

@@

A variable neutrino factory scenario that includes the golden and silver appearance channels can be 
simulated with the file {\tt NF\_GoldSilver.glb}. The basic version was
used within \cite{Huber:2006wb} and the golden channel follows the neutrino factory scenarios from \cite{Huber:2002mx}
and the description of the silver channel follows \cite{Autiero:2003fu}. These
references should be cited if the file {\tt
NFvar\_GoldSilver.glb} is used for a scientific publication or a talk. For calculations that involve {\tt
NFvar\_GoldSilver.glb}, the following additional files are required:
\bi
\item {\tt ThresholdEnergies.dat} (list of energies)
\item {\tt CIDthreshold.dat} (list for CID threshold)
\item {\tt MINOSthreshold.dat} (list for MINOS threshold)
\item {\tt ECCthreshold.dat} (list for ECC threshold)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
and the values of the following {\sf AEDL}-Variables have to be set:
\bi
\item {\tt emax} (parent energy of the stored muons $\left[\mathrm{km}\right]$)
\item {\tt BASELINE} (experiment baseline $\left[\mathrm{GeV}\right]$)
\ei
The beam and golden channel attributes are similar to {\tt NFvar.glb}. The parent energy of the muons can be set
in the range $\mathrm{10\,GeV\lesssim E_\mu\lesssim 80\, GeV}$. The baseline is set by the {\sf
AEDL}-Variable {\tt BASELINE}. For the silver channel, an additional ECC detector with a fiducial mass
$\mathrm{m_{ECC} = 5\,kt}$ is assumed to be located at the same baseline as the MID detector. The energy
resolution of the silver channel is set to $\mathrm{\sigma_e=20\%\cdot E}$. The following additional rule
compared to {\tt NFvar.glb} is introduced in {\tt NF\_GoldSilver.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{$\tau$-Appearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.096 \, \otimes \, (\nu_e \rightarrow \nu_\tau)_\mathrm{CC}$ & & 0.15 & $10^{-4}$ \\
 & & & & \\
Background & $3.1\cdot 10^{-8} \, \otimes \, (\nu_e \rightarrow \nu_e)_\mathrm{CC}$ & $2.0\cdot 10^{-8} \,
\otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.2 & $10^{-4}$ \\ 
 & $3.7\cdot 10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $1.0\cdot 10^{-3} \,
 \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\tau)_\mathrm{CC}$& 0.2 & $10^{-4}$ \\ 
 & $7.0 \cdot 10^{-7} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $7.0\cdot 10^{-7} \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$& 0.2 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

@@

A variable neutrino factory hybrid detector scenario can be simulated with the file {\tt NF\_hR\_lT.glb}. The basic version was
used within \cite{Huber:2006wb} and follows the neutrino factory scenarios from \cite{Huber:2002mx}. These
references should be cited if the file {\tt NF\_hR\_lT.glb} is used for a scientific publication or a talk.
For calculations that involve {\tt NF\_hR\_lT.glb}, the same additional files as for {\tt NFvar.glb} are
required and the {\sf AEDL}-Variables {\tt emax} and {\tt BASELINE} have to be set. {\tt NF\_hR\_lT.glb} 
implements a lower threshold ($\mathrm{\sim\,1\,GeV}$) at a higher energy resolution
$\mathrm{\sigma_e=15\%\cdot E + 0.085\, MeV}$, where the constant term represents 
the effects from Fermi Motion. The background rejection is energy dependent according to 
$10^{-3}/\mathrm{E^2}$, and matches {\tt NFvar.glb} at higher energies. The following rules are defined within {\tt NF\_hR\_lT.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.9 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.2 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^+$-stored} & & \\ \hline
Signal &  $0.5 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.025 & $10^{-4}$ \\
 & & & & \\
Background &  $1.0 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & (energy dep. rejection)
& 0.2 & $10^{-4}$\\
 &  $1.0 \, \otimes \, (\bar{\nu}_\mu \rightarrow\bar{\nu}_\mu)_\mathrm{CC}$ & (energy dep. rejection)
&0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^-$-stored} & & \\ \hline
Signal &  $0.9 \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\bar{\nu}_e
\rightarrow \bar{\nu}_\mu)_\mathrm{CC}$& 0.025& $10^{-4}$\\
 & & & & \\
Background &  $1.0\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^-$-stored} & & \\ \hline
Signal & $0.5 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$  & & 0.025& $10^{-4}$\\
 & & & & \\
Background &  $1.0 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & (energy dep. rejection)
& 0.2 & $10^{-4}$\\
 & $1.0 \, \otimes \, (\nu_\mu \rightarrow
\nu_\mu)_\mathrm{CC}$  & (energy dep. rejection)
&0.2& $10^{-4}$\\ \hline \hline
\end{tabular}
\end{center}

@@

%\end{appendix}
